### 2021-05-12 shared/analysis.tex
feat : Cases of Assert Violation

	double prob, path_prob = 1, choice_prob = 1;
	int sum = 0;

	klee_make_symbolic(&prob, f"prob_sym_{i}");
	for i in range(10):
		int d;
		klee_make_symbolic(&d, f"d_sym_{i}");

@@

\begin{figure}
	\begin{equation}	
		Objective = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) [{x_i} \neq {x_j}]
	\end{equation}
	\caption{Optimization Expression for $k$ randomized paths}
	\label{eq:optimization-1}
\end{figure}

After performing the optimization above, we get different values of $\vec{d_i}$. For $i^{th}$ randomized run. we get a \texttt{single} one hot encoded \texttt{$\vec{d}$} vector. We show below the encoding for a few $i$ values. 
\[
\vec{d}_{1} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]
\[
\vec{d}_{3} = encode(<0,1,0,1,1,0,0,0,1,0>)
\]
\[
\vec{d}_{4} = encode(<1,0,1,0,1,0,1,1,0,1>)
\]
\[
...
\]

We run the optimization by renaming the $k$ \texttt{pse} variables set appropriately and then impose the $distinct$ clause so that we don't run the optimization on the same $randomized$ runs again. \\

For best approximation of the expected value of heads in $n$ trials,
\begin{equation}	
	w_i = \prod_{j=1}^n choice\_prob_{i}(j) ,
	\quad
	sum_i = \sum_{j=1}^n components(\vec{d_i}) ,
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
	\quad
	Error = n * prob - EV(heads)
\end{equation}
where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}

\section{Expression for $k$-paths}

@@

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\end{document}

>>>>

	double prob, path_prob = 1, choice_prob = 1;
	int sum = 0, n = 0;

	klee_make_symbolic(&prob, f"prob_sym_{i}");
	klee_make_symbolic(&n, f"n_symbolic");
	for i in range(n):
		int d;
		klee_make_symbolic(&d, f"d_sym_{i}");

@@

\begin{figure}
	\begin{equation}	
		Objective_1 = maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}}) \quad \mid \forall (i, j) \enspace [{x_i} \neq {x_j}]
	\end{equation}
	\caption{Optimization Expression for $k$ randomized paths}
	\label{eq:optimization-1}
\end{figure}

After performing the optimization above, we get different values of $\vec{d_i}$. For $i^{th}$ randomized run. we get a \texttt{single} one hot encoded \texttt{$\vec{d}$} vector. We show below the encoding for a few $i$ values. 
\[
\vec{d}_{1} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]
\[
\vec{d}_{3} = encode(<0,1,0,1,1,0,0,0,1,0>)
\]
\[
\vec{d}_{4} = encode(<1,0,1,0,1,0,1,1,0,1>)
\]
\[
	....
\]
We run the optimization by renaming the $k$ \texttt{pse} variables set appropriately and then impose the $distinct$ clause so that we don't run the optimization on the same $randomized$ runs again. \\
\begin{equation}	
	\forall (i, j) \enspace [\vec{d_i} \neq \vec{d_j}]
\end{equation} \\
We approximate the value of $expected$ heads in the above program, with the following equations.
\begin{equation}	
	w_i = \prod_{j=1}^n choice\_prob_{i}(j) ,
	\quad
	sum_i = \sum_{j=1}^n components(\vec{d_i}) ,
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
	\quad
	Error = n * prob - EV(heads)
\end{equation}
where both $w_i$ and $sum_i$ can both be computed from the corresponding $\vec{d_i}$ expression we get from the $model$  of the $optimization$ query Eq~\ref{eq:optimization-1}

@@

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.
\end{document}
